disaggregation: An \proglang{R} Package for Bayesian Spatial Disaggregation Modelling

### 2019-12-10 article.Rnw
Remove raster package loading message

%
<<installrun, echo=FALSE, message=FALSE>>=
#devtools::install_github("aknandi/disaggregation")
library(disaggregation, quietly = TRUE)
@
%

>>>>

%
<<installrun, echo=FALSE, message=FALSE>>=
#devtools::install_github("aknandi/disaggregation")
library(disaggregation, quietly = TRUE)
library(raster, quietly = TRUE)
@
%
